SAT Competition 2020\tnoteref{title}

### 2020-12-26 paper/main.tex

\definecolor{gold}{HTML}{FFF3D6}
\definecolor{silver}{HTML}{F3F5F7}
\definecolor{cupper}{HTML}{EAD9D7}
\fboxsep0pt
\newcommand{\firsto}{\colorbox{gold}{$m^1$}}
\newcommand{\firsts}{\colorbox{gold}{$s^1$}}
\newcommand{\firstu}{\colorbox{gold}{$u^1$}}
\newcommand{\firstp}{\colorbox{gold}{$p^1$}}
\newcommand{\secondo}{\colorbox{silver}{$m^2$}}
\newcommand{\seconds}{\colorbox{silver}{$s^2$}}
\newcommand{\secondu}{\colorbox{silver}{$u^2$}}
\newcommand{\secondp}{\colorbox{silver}{$p^2$}}
\newcommand{\thirdo}{\colorbox{cupper}{$m^3$}}
\newcommand{\thirds}{\colorbox{cupper}{$s^3$}}
\newcommand{\thirdu}{\colorbox{cupper}{$u^3$}}
\newcommand{\thirdp}{\colorbox{cupper}{$p^3$}}

@@

\subsection{On the Shoulders of Giants: Popular Code-Bases}
\label{sec:codebases}

@@

The sequential variant to the new code-base \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.

@@

\begin{table}[ht!]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf Team & \bf Base Solver & \bf Variant & \bf Award \\
\hline

\multirow{4}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}} & \multirow{3}{*}{Kissat} &  -- & \firsto\firstu\\
 &  &  sat & \firsto\firstu\seconds\\
 &  &  unsat & \firstu\thirdp\\
\cline{2-4}
 &  Cadical & SC2020 & \\
\hline

\multirow{3}{*}{Zhang, Cai}
    & \multirow{3}{*}{MapleLCMDistCBT-DL} & Relaxed & \\
 &  & Rel. noTimeParam & \\
 &  & Rel. newTech & \secondo\firsts\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{CryptoMiniSat-CCAnr} &  -- & \thirdo\thirds\secondp\\
 &  &  lsids & \thirdo\thirds\secondp\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & CryptoMiniSat-WalkSAT & -- & \\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  trail & \secondu\\
 &  &  alluip & \secondu\firstp\\
 & \multirow{-3}{*}{CaDiCaL} &  alluip-trail & \secondu\firstp\\
 \cline{2-4}
 & MapleLCMDist & alluip-trail & \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistCBT} & f2trc & \thirdu\\
 & & f2trc-s & \thirdu\\
 \cline{2-4}
 & MapleLCMDistCBT-DL & f2trc & \thirdu\\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& MapleLCMDistCBT-DL-v3 & -- & \\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{MapleLCMDistCBT-DL-v3} & Undominated & \\
 &  & Undom. Top16 & \\
 &  & Undom. Top24 & \\
 &  & Undom. Top36 & \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & MapleLCMDistCBT-DL-v3 & DurianSat & \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{MapleLCMDistCBT-DL} & Maple\_Mix & \\
 &  & Maple\_Simp & \\
\hline

Riveros & MapleLCMDistCBT & SLIME & \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{MapleLCMDistCBT-DL} & Scavel & \\
 &  & Scavel01 & \\
 &  & Scavel02 & \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{MapleCoMsPS\_LRB\_VSIDS\_2} & -- & \\
 &  & init & \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{MapleLCMDistCBT-DL-v2.2} & exp-V-LGB & \\
 &  & exp-V-L & \\
 &  & exp-L & \\
 &  & exp-V & \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{MapleCM} & \texttt{+}dist & \\
 &  & \texttt{+}dist\texttt{+}sattime2s\texttt{+}\texttt{-} & \\
 &  & \texttt{+}dist\texttt{+}simp2\texttt{-}\texttt{-} & \\
 &  & used\texttt{+}dist & \\
\hline

Kaiser, Hartung & MapleLCMDist & PauSat & \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{ParaFROST} & -- & \\
 &  & CBT & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Main Tracks (Variant refers to a named configuration or a name of a hack). 
Note that many teams are only responsible for the variant of a previously existing base solver.
Awards were given in Main (m), SAT (s), UNSAT (u), and Planning (p) sub-tracks.}
\label{tab:solvers-main}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & CaDiCaL-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
\label{tab:solvers-incremental}
\end{table}

>>>>

\definecolor{gold}{HTML}{FFF3D6}
\definecolor{silver}{HTML}{F3F5F7}
\definecolor{cupper}{HTML}{EAD9D7}
\fboxsep0pt
\newcommand{\firsto}{\colorbox{gold}{\texttt{M1}}}
\newcommand{\firsts}{\colorbox{gold}{\texttt{s1}}}
\newcommand{\firstu}{\colorbox{gold}{\texttt{u1}}}
\newcommand{\firstp}{\colorbox{gold}{\texttt{P1}}}
\newcommand{\secondo}{\colorbox{silver}{\texttt{M2}}}
\newcommand{\seconds}{\colorbox{silver}{\texttt{s2}}}
\newcommand{\secondu}{\colorbox{silver}{\texttt{u2}}}
\newcommand{\secondp}{\colorbox{silver}{\texttt{P2}}}
\newcommand{\thirdo}{\colorbox{cupper}{\texttt{M3}}}
\newcommand{\thirds}{\colorbox{cupper}{\texttt{s3}}}
\newcommand{\thirdu}{\colorbox{cupper}{\texttt{u3}}}
\newcommand{\thirdp}{\colorbox{cupper}{\texttt{P3}}}

@@

\subsection{Code-Bases of SAT Solvers: ``On the Shoulders of Giants''}
\label{sec:codebases}

@@

The sequential variant of the \emph{new code-base} \solver{ParaFrost} by Osama and Wijs was submitted for the first time in this competition and introduced several interesting new concepts~\cite{Osama:SC2020:Parafrost}.

@@

\renewcommand{\solver}[1]{\underline{\texttt{#1}}}
\newcommand{\solbert}[1]{\texttt{#1}}

\begin{table}[ht!]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf Team & \bf Base Solver & \bf Variant / Name & \bf Award \\
\hline

\multirow{3}{*}{Biere} & \multirow{3}{*}{\solver{Kissat}} &  -- & \firsto, \firstu\\
 &  &  \solbert{sat} & \firsto, \firstu, \seconds\\
 &  &  \solbert{unsat} & \firstu, \thirdp\\
\hline
 Biere, Fleury &  \solbert{Cadical} & \solver{SC2020} & \\
\hline

\multirow{3}{*}{Zhang, Cai}
    & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Relaxed} & \\
 &  & \solbert{Rel. noTimeParam} & \\
 &  & \solbert{Rel. newTech} & \secondo, \firsts\\
\hline

\multirow{2}{*}{\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}}~
 &  \multirow{2}{*}{\solbert{CryptoMiniSat-CCAnr}} &  -- & \thirdo, \thirds, \secondp\\
 &  &  \solbert{lsids} & \thirdo, \thirds, \secondp\\
\hline

\stack{Soos, Selman, Kautz, }{Devriendt, Gocht}~ & \solbert{CryptoMiniSat-WalkSAT} & -- & \\
\hline

\multirow{4}{*}{\stack{Hickey, Feng, }{Bacchus}}
 &  &  \solbert{trail} & \secondu\\
 &  &  \solbert{alluip} & \secondu, \firstp\\
 & \multirow{-3}{*}{\solbert{CaDiCaL}} &  \solver{alluip-trail} & \secondu, \firstp\\
 \cline{2-4}
 & \solbert{MapleLCMDist} & \solver{alluip-trail} & \\
\hline

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{\solbert{MapleLCMDistCBT}} & \solver{f2trc} & \thirdu\\
 & & \solbert{f2trc-s} & \thirdu\\
 \cline{2-4}
 & \solbert{MapleLCMDistCBT-DL} & \solver{f2trc} & \thirdu\\
\hline

\stack{Kochemazov, Zaikin, }{Kondratiev, Semenov} ~& \solver{MapleLCMDistCBT-DL-v3} & -- & \\
\hline

\multirow{4}{*}{\stack{Lonlac, }{Nguifo}}
 & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v3}} & \solver{Undominated} & \\
 &  & \solbert{Undom. Top16} & \\
 &  & \solbert{Undom. Top24} & \\
 &  & \solbert{Undom. Top36} & \\
\hline

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{\solver{Ex}\solbert{MapleLCMDistCBT}} & \solbert{padc\_dl} & \\
 &  & \solbert{padc\_dl\_ovau\_lin} & \\
 &  & \solbert{padc\_dl\_ovau\_exp} & \\
 &  & \solbert{psids\_dl} & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

Shaw, Meel & \solbert{MapleLCMDistCBT-DL-v3} & \solver{DurianSat} & \\
\hline

\multirow{2}{*}{Chen}
 & \multirow{2}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Maple\_Mix} & \\
 &  & \solver{Maple\_Simp} & \\
\hline

Riveros & \solbert{MapleLCMDistCBT} & \solver{SLIME} & \\
\hline

\multirow{3}{*}{Li, Wu, Xu, Chen}
 & \multirow{3}{*}{\solbert{MapleLCMDistCBT-DL}} & \solver{Scavel} & \\
 &  & \solbert{Scavel01} & \\
 &  & \solbert{Scavel02} & \\
\hline

\multirow{2}{*}{\stack{Liang, Oh, Nejati, }{Poupart, Ganesh}}
 & \multirow{2}{*}{\solver{MapleCOMSPS\_LRB\_VSIDS\_2}} & -- & \\
 &  & \solbert{init} & \\
\hline

\multirow{4}{*}{\stack{Chowdhury, }{Müller, You}}
 & \multirow{4}{*}{\solbert{MapleLCMDistCBT-DL-v2.2}} & \solver{exp}\solbert{-V-LGB} & \\
 &  & \solbert{exp-V-L} & \\
 &  & \solbert{exp-L} & \\
 &  & \solbert{exp-V} & \\
\hline

\multirow{4}{*}{\stack{Li, Luo, Xiao, }{Li, Manyà, Lü}}
 & \multirow{4}{*}{\solver{MapleCM}} & \solver{+dist} & \\
 &  & \solbert{+dist+sattime2s+-} & \\
 &  & \solbert{+dist+simp2--} & \\
 &  & \solbert{used+dist} & \\
\hline

Kaiser, Hartung & \solbert{MapleLCMDist} & \solver{PauSat} & \\
\hline

\multirow{2}{*}{Osama, Wijs} 
 & \multirow{2}{*}{\solver{ParaFROST}} & -- & \\
 &  & \solbert{CBT} & \\
\hline
\end{tabular}
\caption[Teams and Solvers in the Main Tracks]{Teams and Solvers in the Main Tracks: In favour of highlighting the relevant branch in the Maple tree of solvers, we identify configuration names of solvers, as well as variants of other base solvers in Column~3 ``Variant / Name''. To avoid confusion, we \solver{underlined} the names of the submitted solvers.}
\label{tab:solvers-main}
\end{table}

\renewcommand{\solver}[1]{\texttt{#1}} % sorry ;)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[ht]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & CaDiCaL-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
\label{tab:solvers-incremental}
\end{table}
